Reduced MHD Notes

### 2024-12-27 Reduced MHD Notes (JB owner)/main.tex
Edits

\documentclass{article}
\usepackage[backend=biber,style=phys]{biblatex}
\addbibresource{references.bib}
\usepackage{gensymb,amsmath,amsthm,amssymb,amsfonts, mathtools, braket, cancel, bm, xcolor}
\usepackage[margin=1in]{geometry}

@@

\subsection{Low-$\beta$ Scaling} \label{lowflow}
In low-$\beta$ scaling ($M_0^2 = 1, \beta_0 = \ep^2$), the limit system is identical to that in high-$\beta$ scaling, and we find that the split $x=(\psi, \nu_\para, \Phi, \Psi, q)$ and $y=(\phi, \beta_\para)$ is weakly fast-slow in exactly the same way.

@@

\begin{equation} \label{frechet}
    Df(u)[h] = \left. \frac{d}{d\ep} \right|_0 f(u+\ep h). 
\end{equation}

>>>>

\documentclass{article}
\usepackage[backend=biber,style=phys]{biblatex}
\addbibresource{references.bib}
\usepackage{amsmath,amsthm,amssymb,amsfonts, mathtools, braket, cancel, bm, xcolor}
\usepackage[margin=1in]{geometry}

@@

\subsection{Low-$\beta$ Scaling} \label{lowbeta}
In low-$\beta$ scaling ($M_0^2 = 1, \beta_0 = \ep^2$), the limit system is identical to that in high-$\beta$ scaling, and we find that the split $x=(\psi, \nu_\para, \Phi, \Psi, q)$ and $y=(\phi, \beta_\para)$ is weakly fast-slow in exactly the same way.

@@

\begin{equation} 
    Df(u)[h] = \left. \frac{d}{d\ep} \right|_0 f(u+\ep h). 
\end{equation}
